Maragra and Malaria: preliminary analysis

### 2017-09-06 inst/rmd/maragra_preliminary_analysis.Rmd
major update

ggplot(data = x,
       aes(x = date,
           y = houses,
           group = insecticida,
           color = insecticida)) +
  geom_point(alpha = 0.6) +
  geom_line(alpha = 0.6) +
  theme_maragra() +
  labs(x = 'Month',
       y = 'Houses fumigated',
       title = 'Maragra IRS activity by insecticide type over time') +
  scale_color_manual(name = 'Chemical',
                     values = cols)
```

>>>>

ggplot(data = x,
       aes(x = date,
           y = houses,
           group = insecticida,
           color = insecticida)) +
  geom_point(alpha = 0.6) +
  geom_line(alpha = 0.6) +
  theme_maragra() +
  labs(x = 'Month',
       y = 'Houses fumigated',
       title = 'Maragra IRS activity by insecticide type over time') +
  scale_color_manual(name = 'Chemical',
                     values = cols) +
  geom_vline(xintercept = as.numeric(as.Date(paste0(2012:2017, '-01-01'))),
             alpha = 0.2)
```
